---
title: "Getting Started with PAMvieweR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with PAMvieweR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PAMvieweR)
```

# New Occurrence R6 Class

First things first. You'll need to set up a connection to `nefscdb1`, which is the database where the `PAGROUP` schema lives (colloquially known as Makara).

```{r db, eval = FALSE}
# db connection
db_conn <- ROracle::dbConnect(ROracle::Oracle(), 
                              dbname = 'NEFSC_USERS',
                              username = '[uid]', 
                              password = '[pwd]')
```

Once you've established a db connection, you can get started by generating an object with an `Occurrence` R6 class. For those familiar with python, the syntax of R6 classes should feel familiar. For those more acquainted with R, R6 classes will take some getting used to. A good resource on R6 classes can be found [here](https://r6.r-lib.org/articles/Introduction.html).

In order to initialize an object with an `Occurrence` class, we must provide 2 arguments: 1) a db connection and 2) the name of data table / view we're interested in pulling data from. For example,

```{r occ, eval = FALSE}
# new Occurrence object
huwh_occ <- Occurrence$new(connection = db_conn, table = 'V_PRJCT_DPLYMNT_DTCTN_O')
```


